Dynamical Properties of Molecular Cloud Complexes in Galaxies at the Epoch of Reionization

### 2019-03-30 WRITEUP/ms.tex
finished sec 6 comments.  This completes my comments and revisions for the moment.

We show in \Fig{dist} the MCC distribution in terms of their molecular gas mass, radius, and gas mass fraction, which we define as
\begin{equation}
f_{\rm gas} = \frac{M_{\rm cl}} {\left(M_{\rm cl} + M_\star\right)},
\end{equation}
where $M_\star$ is the stellar mass within the MCC volume.
%
We note that the distributions vary for different evolutionary stages of \flower. The highest density threshold of $n_{\rm cut}$\eq31.62\,\cc yields a minimum MCC mass of the order of 10$^{5.5}$\,\Msun for the densest MCC.
%
We find $\sim$10--13 MCCs with masses exceeding 10$^8$\,\Msun across
all the evolutionary stages considered in this work, for each  $n_{\rm
  cut}$ value. \AF{This is true only for low $n_{cut}$? Why in Fig. do
  you show the valu 18.96 instead?} \DL{MCCs w/ Mcl $>$10$^8$\,\Msun
  is the case for each ncut.} \MM{I am afraid I am also confused by
  this, for two reasons.  First, if I understand the Figure, the
  highest $n_{\rm cut}$ shows no such large MCCs at any time.  Second,
  back in section 3, the H$_2$ mass of \flower was given as 5\E7
  \Msun, precluding the existence of even a single 10$^8$ \Msun
  cloud.} 
\DL{Since we don't resolve the molecular clouds, the clouds are not fully molecular. The $M_{\rm cl}$ here is more 
like total gas mass. AP will add disclaimer in Section 3. Will double check 
Mcl for all ncut and address AF's comment.}
  Such massive clouds correspond to the molecular disk of the
galaxy, which is identified as a single component for low $n_{\rm
  cut}$. The mass of the MCCs identified ranges between $M_{\rm
  cl}\simeq$10$^{5.5-8.5}$\,\Msun, consistent with those observed in
\z$\sim$2 galaxies in rest-frame UV and optical light
\citep{Elmegreen07a, Elmegreen09a}. \AF{you do not comment on $R$ and
  $f_{gas}$ here..Also, what is the total number of MCCs?} \MM{In the
  high-density plot, it looks like you have quite a number of
  unresolved clouds with $R < 40$~pc. Any idea what's going on there?}

@@

The MCCs of \flower have dynamics largely similar to those observed in
$z$\ssim2 spatially resolved studies of gas-rich star-forming
galaxies, in terms of their velocity dispersions, sizes, and gas
surface densities (\Fig{larsons_single}; see e.g.,
\citealt{Swinbank11a}), with sizes of the order of $R\simeq$\,100\,pc
and velocity dispersions of $\sigma\simeq$\,20$-$80\,\kms. 
\MM{They agree in $\sigma$ vs.\ $R$, but their virial parameters seem
  high compared to the data sets provided, particularly for their
  relatively low surface densities (Figs.\ 5, 6).}
%
% velocity dispersion, larsons
%
Their velocity dispersions are also comparable to those observed in the inner Milky way and nearby gas-rich galaxies (e.g., M64; \citealt{Oka01a, Rosolowsky05a, Heyer09a}), which lies along the locus of $\sigma\propto R^{0.56}$. Such high velocity dispersions and surface densities are expected since they are located in the nuclear regions of the galaxy, where the potential well is also deep. The higher velocity dispersions
(see footnote~\ref{ftn:veldisp} on page \pageref{ftn:veldisp}) of
these MCCs can also be understood as they have experienced more recent
episodes of \SF as \flower is assembling its stellar mass (these MCCs
also have higher stellar-to-gas mass ratios of $\sim$60). \MM{This is
  an enormous stellar to gas mass ratio, suggesting the clouds are
  completely controlled by the gravitational potential of the stars.
  A normal molecular cloud would have a ratio of < 0.1!  The
  implications of this for the apparent virial parameters and velocity
dispersions need to be considered much more carefully than they have been.}
%
In fact, by the accretion stage (see \Fig{SFH}a) at $z\simeq$\,7.2, 
\flower has assembled a stellar mass of $M_\star$\eq7.5\E{9}\,\Msun. Thus, the higher velocity dispersion is due in part to the stronger stellar feedback compared to e.g., MCCs in its satellites ($\sigma\simeq$10\,\kms).

The high pressure observed in \flower is comparable to what has been observed in local ultra-luminous IR galaxies (ULIRGs); however, the molecular clouds in the latter are concentrated within their central regions and have typical sizes of $\sim$70-100\,pc and masses on the order of $\sim$10$^9$\,\Msun \citep{Downes98a, Sakamoto08a}. In our simulated galaxy, the high pressure MCCs of \flower are found throughout the disk. This difference likely stems from the different physical mechanisms giving rise to the formation (and thus the nature) of these molecular structures.
%
For instance, in local ULIRGs, they are likely form by shock compression and cloud-cloud collision after large amount of gas from the pair of progenitor galaxies are being funneled toward the central region \citep{Tan00a, Wu18a}.
% Tasker09a
On the other hand, the highly turbulent structures of \flower likely result from 
extra-planar flows that are due to gas accretion onto the galaxy and SN-driven outflows \citep{gallerani:2018,kohandel:2019}.
The presence of such extra-planar flows may also be the 
dominant mode for forming the highly supersonic massive MCCs observed in gas-rich star-forming galaxies at $z$\ssim2 (see also e.g., \citealt{Swinbank11a}) --- but the observed size scales could also result from resolution limit where the true physical scales of MCCs in $z$\,\ssim2 galaxies could be smaller in reality.
%
The constant inter-cloud collision as gas is being accreted onto the main galaxy would also render
the MCCs to be gravitationally unbound (see e.g., \citealt{Dobbs11a}), which is
consistent with the high $\alpha_{\rm vir}$ found for the MCCs in the main disk of \flower.

% mass-size relation
MCCs of \flower lie below the locus of $A_V$\eq100\,mag followed by Milky Way clouds in the mass-size relation shown in \Fig{MR}. This can be understood by acknowledging the fact that a H$_2$ molecular cloud does not necessary contain CO (e.g., as CO forms deeper in molecular clouds), and that our simulation does not have enough resolution to directly form CO\footnote{In fact, to form CO and make predictions for CO line emission in the work presented by \citet{Vallini18a}, we model the internal structure of MCC within each cell in our simulation.}.
%
That is, the MCCs of \flower lying along the locus of $A_V$\eq4\,mag likely manifests from the fact that the MCCs in our simulation have lower column densities than the star-forming cores observed in the Milky Way, which are observationally well-resolved within an MCC, and indeed, have sufficient column density to form CO.

The \citet{Kauffmann10c} relation suggests that regions with high-mass \SF follow 
an ``internal'' mass-size relation where $M\propto R^{1.33}$.
If this holds for MCCs of \flower, an extrapolation of the \citet{Kauffmann10c} relation down to $\sim$1\,pc would correspond to structures with masses and sizes comparable to those of the cores found in
regions of high-mass \SF. That is, the MCCs identified have mass-size relations suggesting they are capable of high-mass \SF.

% different evolutionary stages
In the scaling relations examined, we find similar MCC properties in relation to those observed in the nearby Universe between the accretion phase and the starburst phase of \flower (see \Fig{larsons_single}). That is, we do not find any quantitative major differences in the MCC properties between the accretion and the starburst phase, which are separated by $\simeq$300\,Myr. \DL{some MCCs in SB phase have
lower $\alpha_{\rm vir}$ and pressure, but 
is there any significance in that?}

@@

The largest molecular structure identified is essentially the main
disk of \flower and breaks down into smaller substructures that are
denser as we increase $n_{\rm cut}$ (see e.g.,
\Fig{alpha16-28}). Overall, the MCCs we identified are much bigger in
size and mass than nearby giant molecular clouds (GMCs), but comparable to those observed in $z$\,\ssim2$-$4 galaxies based on spatially resolved imaging \citep{Swinbank11a}.

% mass scale
Observations of nearby gas-rich galaxies such as M64 and NGC\,253 show higher velocity dispersions compared to the disk/mid-plane of the Milky Way but consistent with those observed in the inner regions of Milky Way and M51 \citep{Oka01a, Rosolowsky05a, Heyer09a, Hughes13b, Leroy15a, Rice16a}.  % also higher $P_{\rm int}$,
% which is $\propto\rho\sigma^2$
% M51: Colombo+14
However, clouds in nearby gas-rich galaxies are bigger in size (approximately an order of magnitude) and mass (approximately two orders of magnitude).
These bigger clouds have been interpreted as a result of their higher gas mass fractions, surface densities, and velocity dispersions,
since fragmentation occurs near the Jeans length $L_J\propto\sigma^2/\Sigma$ and
Jeans mass $M_J\propto\sigma^4/\Sigma$ for dispersion-supported structures.

Based on the scaling of $M_J$\eq$\sigma^4/(G^2\Sigma)$ for the Jeans mass, a
velocity dispersion of $\sigma\simeq50$\,\kms and a
gas mass surface density of $\Sigma_{\rm gas}\simeq450$\,\Msun\,pc$^{-2}$ yields
$M_J\sim$\,8\E{8}\,\Msun, which is in good agreement with the mass range found in the MCCs identified (see \Fig{dist}).
%
Similarly massive molecular clouds have been reported in idealized closed-box isolated galaxy simulations done at higher resolution (e.g., a maximum
resolution of 3\,pc in the 48\,kpc box studied by \citealt{Behrendt16a}).
Note, however, that the IGM and merger and accretion histories are not properly modeled in such simulations since they adopt non-cosmological initial conditions. That said, this is reassuring --- our results are not far off in spite of the limited resolution ($l_{\rm cell}\simeq$\,30\,pc).

@@

% alpha parameters
As shown in \Fig{larsons_single},
the virial parameter of the sub-MCCs is about $\alpha_{\rm vir}\gtrsim10$, which is considerably lower than their ``parent'' MCCs found in the main disk of \flower ($\alpha_{\rm vir}\gtrsim100$).
%
For the MCCs in the satellite galaxies, a lower virial parameter is found compared to the (sub-)MCCs in the main disk of \flower, with $\alpha_{\rm vir}\simeq$\,2.
Differences in their $\alpha_{\rm vir}$ most likely result from the weaker stellar feedback in the satellites as they have experienced less episodes of \SF compared to \flower (i.e., lower stellar-to-gas mass ratios of $\sim$0.1).

% pext
As shown in \Fig{larsons_single},
MCCs in the main disk of \flower have higher pressure than the sub-MCCs. The lower virial parameter and external pressure of the sub-MCCs compared to their parent MCCs are consistent with the notion that collapsing structures result from local gravitational instability within globally non-collapsing structures \citep[see e.g.,][]{Ballesteros-Paredes11a}, which are supported by turbulence and rotation on large scales.
%Based on the virial parameter, velocity dispersion, and pressure of the MCC identified in the main disk of \flower,
%the MCC itself is gravitationally unbound and supported by turbulence (from the feedback of multiple episodes of \SF)
%and galactic rotation on large scales.
%% Turbulence in these substructures further dissipates in % e.g., shocks on even smaller scales, allowing sub-MCCs to be bound and collapse.

For MCCs in the satellite galaxies, we find even lower pressures and virial parameters, which are comparable to those found in clouds formed in the galactic disks  ($\alpha_{\rm vir}$\eq0.2$-$10; \citealt{Dobbs08a, Tasker09a}).
This suggests that MCCs identified in the satellite galaxies are likely to be collapsing structures, and thus, \SF is expected to continue as gas from satellite galaxies is being accreted onto the main galaxies during the EoR.

@@

\begin{figure*}
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.92\textwidth]{\figpath/{ss16_toomre_combined_3by1_0_2.0}.pdf}
\includegraphics[trim=0 0 0 65, clip, width=0.95\textwidth]{\figpath/{ss16_toomre_combined_3by1_0_0.8}.pdf}
\caption{
Toomre $Q$ maps derived from the
central $r$\eq2\,kpc (top row) and $r$\eq0.8\,kpc (bottom row) of \flower.
Gas-only $Q_{\rm gas}$ are shown in the left panels and stellar-only $Q_\star$ are shown in the middle panels.
Maps of the effective two-component Toomre $Q_{\rm eff}$ parameter are shown in the right panels.
All maps are projected onto the $xy$-plane.
Positions of MCCs identified with $n_{\rm cut}$\eq6.81\,cm$^{-3}$ are overplotted as star symbols.
A smoothing length of 30\,pc has been applied to the maps.
A divergent colormap is used for the Toomre $Q$ maps to facilitate
identification of regions above and below $\log{Q}$\eq0.
Some MCCs lie in regions of $\log{Q_{\rm eff}}\gtrsim0$, where regions of $\log{Q_{\rm eff}}\lesssim0$
are likely gravitationally unstable.
Close resemblance of the $Q_\star$ and $Q_{\rm eff}$ maps in the central region of \flower 
indicates that stellar component plays an important role in governing the stability of the MCCs against $m=0$  perturbations, highlighting the importance of accounting for stellar contribution when examining the stability of molecular gas in relatively evolved and enriched systems at high redshifts.
\label{fig:Qeff}}
\end{figure*}

@@

That is, some MCCs are found in regions of $Q_{\rm gas}$\ssim1, consistent with the expectation that they correspond to regions of high surface densities that are gravitationally unstable. 
Note, however, that when including the stabilizing effects due to the stellar potential of \flower and the
thickness of its disk (via $\sigma_z$), some of these MCCs are consistent with  $Q_{\rm eff} > 1$. 
This demonstrates the importance of accounting for stellar contribution and disk thickness 
when examining the stability of molecular gas structures.
This consideration is especially relevant for the relatively evolved and enriched systems at high-$z$, 
that are preferentially being imaged at high resolution with ALMA.
In the outer regions of \flower, on the other hand, $Q_{\rm eff}$ resembles $Q_{\rm gas}$, with 
both $\log{Q_{\rm gas}}$ and $\log{Q_{\rm eff}} < -1$. 
Notably, these are the more gas-rich regions (see \Fig{sigma}).

@@

Note that even in stages when \flower~is star forming we find that most of its MCCs have high $\alpha_{\rm vir}$. This seem to be self-contradictory: if most of the molecular gas in \flower are stable against collapse, how does it sustain its high SFR of $\sim$70\,\Msun\,yr\pmOne in the starburst phase? Such tension in the interpretation is understood as follows.
%
First, our results are limited by the resolution of the simulation, i.e., in \flower~we do not resolve \SF in {\it cores} and {\it clumps} as in the classical molecular cloud hierarchy. This re-iterates the statement about low $Q$ above.
%
Second, due to turbulence dissipation on small-scales, such (sub-)structures are no longer supported by large-scale gravitational potential and differential rotation. This in turn enables sub-regions of the MCCs to collapse and potentially form OB associations out of these unbound MCCs \citep{Clark04a, Clark05a}.
%
Further, mechanisms causing non-axisymmetric perturbations (e.g., arms) to the gravitational potential can induce orbit crossing, shocks and dissipation in gas, promoting turbulence dissipation and collapse on smaller scales to trigger \SF. These mechanisms are likely important given high $Q_{\rm eff}$ found across \flower and its few tens of solar masses per year SFR, albeit sporadic.
Finally, the SFR of \flower is very bursty and high SFR stages are only transient.
% the giant MCCs found are likely due to non-axisymmetric mode.

>>>>

We show in \Fig{dist} the MCC distribution in terms of their molecular gas mass, radius, and gas mass fraction, which we define as
\begin{equation}
f_{\rm gas} = \frac{M_{\rm cl}} {\left(M_{\rm cl} + M_\star\right)},
\end{equation}
where $M_\star$ is the stellar mass within the MCC volume.
%
We note that the distributions vary for different evolutionary stages of \flower. The highest density threshold of $n_{\rm cut}$\eq31.62\,\cc yields a minimum MCC mass of the order of 10$^{5.5}$\,\Msun for the densest MCC.
%
We find $\sim$10--13 MCCs with masses exceeding 10$^8$\,\Msun across
all the evolutionary stages considered in this work, for each  $n_{\rm
  cut}$ value. \AF{This is true only for low $n_{cut}$? Why in Fig. do
  you show the valu 18.96 instead?} \DL{MCCs w/ Mcl $>$10$^8$\,\Msun
  is the case for each ncut.} \MM{I am afraid I am also confused by
  this, for two reasons.  First, if I understand the Figure, the
  highest $n_{\rm cut}$ shows no such large MCCs at any time.  Second,
  back in section 3, the H$_2$ mass of \flower was given as 5\E{7}
  \Msun, precluding the existence of even a single 10$^8$ \Msun
  cloud.} 
\DL{Since we don't resolve the molecular clouds, the clouds are not fully molecular. The $M_{\rm cl}$ here is more 
like total gas mass. AP will add disclaimer in Section 3. Will double check 
Mcl for all ncut and address AF's comment.}
  Such massive clouds correspond to the molecular disk of the
galaxy, which is identified as a single component for low $n_{\rm
  cut}$. The mass of the MCCs identified ranges between $M_{\rm
  cl}\simeq$10$^{5.5-8.5}$\,\Msun, consistent with those observed in
\z$\sim$2 galaxies in rest-frame UV and optical light
\citep{Elmegreen07a, Elmegreen09a}. \AF{you do not comment on $R$ and
  $f_{gas}$ here..Also, what is the total number of MCCs?} \MM{In the
  high-density plot, it looks like you have quite a number of
  unresolved clouds with $R < 40$~pc. Any idea what's going on there?}

@@

The MCCs of \flower have dynamics largely similar to those observed in
$z$\ssim2 spatially resolved studies of gas-rich star-forming
galaxies, in terms of their velocity dispersions, sizes, and gas
surface densities (\Fig{larsons_single}; see e.g.,
\citealt{Swinbank11a}), with sizes of the order of $R\simeq$\,100\,pc
and velocity dispersions of $\sigma\simeq$\,20$-$80\,\kms. 
\MM{They agree in $\sigma$ vs.\ $R$, but their virial parameters seem
  high compared to the data sets provided, particularly for their
  relatively low surface densities (Figs.\ 5, 6).}
%
% velocity dispersion, larsons
%
Their velocity dispersions are also comparable to those observed in the inner Milky way and nearby gas-rich galaxies (e.g., M64; \citealt{Oka01a, Rosolowsky05a, Heyer09a}), which lies along the locus of $\sigma\propto R^{0.56}$. Such high velocity dispersions and surface densities are expected since they are located in the nuclear regions of the galaxy, where the potential well is also deep. The higher velocity dispersions
(see footnote~\ref{ftn:veldisp} on page \pageref{ftn:veldisp}) of
these MCCs can also be understood as they have experienced more recent
episodes of \SF as \flower is assembling its stellar mass (these MCCs
also have higher stellar-to-gas mass ratios of $\sim$60). \MM{This is
  an enormous stellar to gas mass ratio, suggesting the clouds are
  completely controlled by the gravitational potential of the stars.
h  A normal molecular cloud would have a ratio of < 0.1!  The
  implications of this for the apparent virial parameters and velocity
dispersions need to be considered much more carefully than they have been.}
%
In fact, by the accretion stage (see \Fig{SFH}a) at $z\simeq$\,7.2, 
\flower has assembled a stellar mass of
$M_\star$\eq7.5\E{9}\,\Msun. Thus, the higher velocity dispersion is
due in part to the stronger stellar feedback \MM{Again, not clear that
  this is feedback and not potential driven. Can you demonstrate one
  or the other explicitly?} compared to e.g., MCCs in
its satellites ($\sigma\simeq$10\,\kms) \MM{This needs to be shown in
  a Figure, not just asserted}.

The high pressure observed in \flower \MM{Where are pressures shown?
  You can't just draw them from the virial vs.\ surface density plot
  because that assumes equilibrium gas clouds, which these are clearly
  not, given their huge stellar contents.} is comparable to what has been observed in local ultra-luminous IR galaxies (ULIRGs); however, the molecular clouds in the latter are concentrated within their central regions and have typical sizes of $\sim$70-100\,pc and masses on the order of $\sim$10$^9$\,\Msun \citep{Downes98a, Sakamoto08a}. In our simulated galaxy, the high pressure MCCs of \flower are found throughout the disk. This difference likely stems from the different physical mechanisms giving rise to the formation (and thus the nature) of these molecular structures.
%
For instance, in local ULIRGs, 
%mm they are likely form 
  MCCs are likely formed
by shock compression and cloud-cloud collisions 
%mm after large amounts of gas from the pair of progenitor galaxies
%are funneled toward the central region 
    that funnel large amounts of gas from the progenitor galaxies
    towards the central region
\citep{Tan00a, Wu18a}.
% Tasker09a
On the other hand, the highly turbulent structures of \flower likely result from 
extra-planar flows that are due to gas accretion onto the galaxy and SN-driven outflows \citep{gallerani:2018,kohandel:2019}.
The presence of such extra-planar flows may \MM{Do we have any
  evidence for or against this speculation?} also be the 
dominant mode for forming the highly supersonic massive MCCs observed
in gas-rich star-forming galaxies at $z$\ssim2 (see also e.g.,
\citealt{Swinbank11a}) --- but the observed size scales could also
result from the resolution limit, while the true physical scales of
MCCs in $z$\,\ssim2 galaxies could be smaller.
%mm in reality.
%
The constant inter-cloud collisions as gas is being accreted onto the
main galaxy \MM{This is a highly dissipative process.  Hennebelle \&
  Klessen found it could only be important in rather small galaxies.
  Does \flower qualify?} would also render
the MCCs 
%mm to be 
gravitationally unbound (see e.g., \citealt{Dobbs11a}), \MM{Dobbs
  started with a low-density disk, and got low-density clouds. I don't
  think that's what you have here.  Do you have any evidence for
  inter-cloud collisions being important?} which is
consistent with the high $\alpha_{\rm vir}$ found for the MCCs in the main disk of \flower.

% mass-size relation
The MCCs of \flower lie below the locus of $A_V$\eq100\,mag followed
by Milky Way clouds in the mass-size relation shown in \Fig{MR}. This
can be understood by acknowledging the fact that a H$_2$ molecular
cloud does not necessary contain CO (e.g., as CO forms deeper in
molecular clouds), and that our simulation does not have enough
resolution to directly form CO\footnote{In fact, to form CO and make
  predictions for CO line emission in the work presented by
  \citet{Vallini18a}, we model the internal structure of MCC within
  each cell in our simulation.}.  
\MM{But column densities have nothing to do with CO, and you are
  deriving $A_V$ from column densities.  Forming CO doesn't increase
  column densities; it is just a tracer of dense gas.  Atomic line
  cooling will be just as efficient as CO in actually cooling the gas
  down to tens of Kelvin (see Clark \& Glover some years ago).}
%
That is, the MCCs of \flower lying along the locus of $A_V$\eq4\,mag 
%mm likely manifests from the fact 
    demonstrates
that the MCCs in our simulation have lower column densities than the
star-forming cores observed in the Milky Way, which are
observationally well-resolved within an MCC, and indeed, have
sufficient column density to form CO.  \MM{I suppose the question is
  if we observed the Milky Way at equivalent resolution, would we see
  such low column densities on average?  This is more or less the game
that Diderijk Kruijssen has been playing.}

The \citet{Kauffmann10c} relation suggests that regions with high-mass \SF follow 
an ``internal'' mass-size relation where $M\propto R^{1.33}$.
If this holds for the MCCs of \flower, an extrapolation of the \citet{Kauffmann10c} relation down to $\sim$1\,pc would correspond to structures with masses and sizes comparable to those of the cores found in
regions of high-mass \SF. That is, the MCCs identified have mass-size
relations suggesting they are capable of high-mass \SF. \MM{I don't
  yet understand how this squares with their very high virial
  parameters and large stellar contents.}

% different evolutionary stages
In the scaling relations examined, we find similar MCC properties in
relation to those observed in the nearby Universe between the
accretion phase and the starburst phase of \flower (see
\Fig{larsons_single}). \MM{I'm not entirely sure what this sentence is
  trying to say.  These MCCs don't look similar to nearby objects to
  me... but then you make a comparison between phases?} That is, we do not find any quantitative major differences in the MCC properties between the accretion and the starburst phase, which are separated by $\simeq$300\,Myr. \DL{some MCCs in SB phase have
lower $\alpha_{\rm vir}$ and pressure, but 
is there any significance in that?} \MM{I'd say there is great
significance to that: lower $\alpha_{\rm vir}$ means greater ability to form
stars, exactly what would be expected during a starburst.}

@@

The largest molecular structure identified is essentially the main
disk of \flower \MM{Is this consistent with your assertion of no shear
  in a footnote above?} and breaks down into smaller substructures that are
denser as we increase $n_{\rm cut}$ (see e.g.,
\Fig{alpha16-28}). Overall, the MCCs we identified are much bigger in
size and mass than nearby giant molecular clouds (GMCs), but comparable to those observed in $z$\,\ssim2$-$4 galaxies based on spatially resolved imaging \citep{Swinbank11a}.

% mass scale
Observations of nearby gas-rich galaxies such as M64 and NGC\,253 show
higher velocity dispersions compared to the disk
%mm/mid-plane 
of the Milky Way but consistent with those observed in the inner regions of Milky Way and M51 \citep{Oka01a, Rosolowsky05a, Heyer09a, Hughes13b, Leroy15a, Rice16a}.  % also higher $P_{\rm int}$,
% which is $\propto\rho\sigma^2$
% M51: Colombo+14
However, clouds in nearby gas-rich galaxies are bigger in size (approximately an order of magnitude) and mass (approximately two orders of magnitude).
These bigger clouds have been interpreted as 
%mm a result of their higher gas mass fractions, [I had trouble
%interpreting this sentence. Do you agree with the revision?]
    forming because of the higher gas fractions in these galaxies,
    which lead to higher
surface densities, and 
%mm velocity dispersions
   ultimately velocity dispersions as collapse occurs.
Fragmentation occurs near the Jeans length $L_J\propto\sigma^2/\Sigma$ and
Jeans mass $M_J\propto\sigma^4/\Sigma$ for dispersion-supported structures.

Based on the scaling of $M_J$\eq$\sigma^4/(G^2\Sigma)$ for the Jeans mass, a
velocity dispersion of $\sigma\simeq50$\,\kms and a
gas mass surface density of $\Sigma_{\rm gas}\simeq450$\,\Msun\,pc$^{-2}$ yields
$M_J\sim$\,8\E{8}\,\Msun, which is in good agreement with the mass
range found in the MCCs identified (see \Fig{dist}).  \MM{I really
  don't see this: \Fig{dist} has no clouds that massive, and in
  the higher density case doesn't even get within an order of
  magnitude of this value.  In both cases, the mode is closer to 5\E{6} \Msun.}
%
Similarly massive \MM{8\E{8} \Msun?} molecular clouds have been reported in idealized closed-box isolated galaxy simulations done at higher resolution (e.g., a maximum
resolution of 3\,pc in the 48\,kpc box studied by \citealt{Behrendt16a}).
Note, however, that the IGM and merger and accretion histories are not properly modeled in such simulations since they adopt non-cosmological initial conditions. That said, this is reassuring --- our results are not far off in spite of the limited resolution ($l_{\rm cell}\simeq$\,30\,pc).

@@

% alpha parameters
As shown in \Fig{larsons_single},
the virial parameter of the sub-MCCs \MM{How can we distinguish
  sub-MCCs from MCCs in this figure?} is $\alpha_{\rm vir}\gtrsim10$,
which is considerably lower than their ``parent'' MCCs found in the
main disk of \flower ($\alpha_{\rm vir}\gtrsim100$).  \MM{However,
  both are extremely high.}
%
For the MCCs in the satellite galaxies, \MM{How can we distinguish
  these, in turn?} a lower virial parameter is found compared to the (sub-)MCCs in the main disk of \flower, with $\alpha_{\rm vir}\simeq$\,2.
Differences in their $\alpha_{\rm vir}$ most likely result from the
weaker stellar feedback in the satellites \MM{Or lower stellar content
and thus weaker potentials?} as they have experienced fewer episodes
of \SF compared to \flower (i.e., lower stellar-to-gas mass ratios of
$\sim$0.1) \MM{This is what I would expect for molecular gas.  Should
  you explicitly show stellar-to-gas mass ratios in a figure?}.

% pext
As shown in \Fig{larsons_single},
MCCs in the main disk of \flower have higher pressure than the
sub-MCCs. \MM{Pressures are not shown in this figure, as noted
  above. If you want to demonstrate pressure, you need to actually
  examine the gas pressure field.} The lower virial parameter and external pressure of the sub-MCCs compared to their parent MCCs are consistent with the notion that collapsing structures result from local gravitational instability within globally non-collapsing structures \citep[see e.g.,][]{Ballesteros-Paredes11a}, which are supported by turbulence and rotation on large scales.
%Based on the virial parameter, velocity dispersion, and pressure of the MCC identified in the main disk of \flower,
%the MCC itself is gravitationally unbound and supported by turbulence (from the feedback of multiple episodes of \SF)
%and galactic rotation on large scales.
%% Turbulence in these substructures further dissipates in % e.g., shocks on even smaller scales, allowing sub-MCCs to be bound and collapse.

For MCCs in the satellite galaxies, we find even lower pressures and
virial parameters, \MM{This needs to be shown explicitly in a figure,
  as I think I already mentioned above.} which are comparable to those found in clouds formed in the galactic disks  ($\alpha_{\rm vir}$\eq0.2$-$10; \citealt{Dobbs08a, Tasker09a}).
This suggests that MCCs identified in the satellite galaxies are likely to be collapsing structures, and thus, \SF is expected to continue as gas from satellite galaxies is being accreted onto the main galaxies during the EoR.

@@

\begin{figure*}
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.92\textwidth]{\figpath/{ss16_toomre_combined_3by1_0_2.0}.pdf}
\includegraphics[trim=0 0 0 65, clip, width=0.95\textwidth]{\figpath/{ss16_toomre_combined_3by1_0_0.8}.pdf}
\caption{
Toomre $Q$ maps derived from the
central $r$\eq2\,kpc (top row) and $r$\eq0.8\,kpc (bottom row) of \flower.
Gas-only $Q_{\rm gas}$ is shown in the left panels and stellar-only $Q_\star$ is shown in the middle panels.
Maps of the effective two-component Toomre $Q_{\rm eff}$ parameter are shown in the right panels.
All maps are projected onto the $xy$-plane.
Positions of MCCs identified with $n_{\rm cut}$\eq6.81\,cm$^{-3}$ are overplotted as star symbols.
A smoothing length of 30\,pc has been applied to the maps.
A divergent colormap is used for the Toomre $Q$ maps to facilitate
identification of regions above and below $\log{Q}$\eq0.
Some MCCs \MM{But these are the exception.} lie in regions of $\log{Q_{\rm eff}}\gtrsim0$, where regions of $\log{Q_{\rm eff}}\lesssim0$
are likely gravitationally unstable.
Close resemblance of the $Q_\star$ and $Q_{\rm eff}$ maps in the central region of \flower 
indicates that the stellar component plays an important role in
governing the stability of the MCCs against $m=0$  perturbations,
\MM{Well, there are definitely regions dominated by gas.}  highlighting the importance of accounting for stellar contribution when examining the stability of molecular gas in relatively evolved and enriched systems at high redshifts.
\label{fig:Qeff}}
\end{figure*}

@@

That is, some MCCs are found in regions of $Q_{\rm gas}$\ssim1, consistent with the expectation that they correspond to regions of high surface densities that are gravitationally unstable. 
Note, however, that when including the stabilizing effects due to the stellar potential of \flower and the
thickness of its disk (via $\sigma_z$), some of these MCCs are
consistent with  $Q_{\rm eff} > 1$. 
\MM{Is your $Q_{\rm eff}$ based on your equation 11?  If not, you
  should probably show it's value explicitly, or else remove that
  section of the explanation [you don't want to leave the ``rifle on
  the wall''.]}.
This demonstrates the importance of accounting for stellar contribution and disk thickness 
when examining the stability of molecular gas structures.
This consideration is especially relevant for the relatively evolved and enriched systems at high-$z$, 
that are preferentially being imaged at high resolution with ALMA.
In the outer regions of \flower, on the other hand, $Q_{\rm eff}$ resembles $Q_{\rm gas}$, with 
both $\log{Q_{\rm gas}}$ and $\log{Q_{\rm eff}} < -1$. 
Notably, these are the more gas-rich regions (see \Fig{sigma}).

@@

Note that even in stages when \flower~is star forming we find that most of its MCCs have high $\alpha_{\rm vir}$. This seem to be self-contradictory: if most of the molecular gas in \flower are stable against collapse, how does it sustain its high SFR of $\sim$70\,\Msun\,yr\pmOne in the starburst phase? Such tension in the interpretation is understood as follows.
%
First, our results are limited by the resolution of the simulation, i.e., in \flower~we do not resolve \SF in {\it cores} and {\it clumps} as in the classical molecular cloud hierarchy. This re-iterates the statement about low $Q$ above.
%
Second, due to turbulence dissipation on small-scales, such
(sub-)structures are no longer supported by large-scale gravitational
potential and differential rotation.  \MM{Not sure how potential can
  support, and in that footnote above you asserted that shear was
  unimportant, contradicting this claim.} This in turn enables sub-regions of the MCCs to collapse and potentially form OB associations out of these unbound MCCs \citep{Clark04a, Clark05a}.
%
Further, mechanisms causing non-axisymmetric perturbations (e.g.,
arms) to the gravitational potential \MM{Gravitational instability is
  that mechanism (see e.g.\ Wada et al.'s classic review of the
  subject (2011, doi:10.1017/S1743921311000640), so this isn't really a separate mechanism.} can induce orbit crossing, shocks and dissipation in gas, promoting turbulence dissipation and collapse on smaller scales to trigger \SF. These mechanisms are likely important given high $Q_{\rm eff}$ found across \flower and its few tens of solar masses per year SFR, albeit sporadic.
Finally, the SFR of \flower is very bursty and high SFR stages are only transient.
% the giant MCCs found are likely due to non-axisymmetric mode.
